\vspace*{-2.5cm} \hspace*{-0.5cm}Online platformazation and Offline expansion of Real Estate Brokerage: Evidence from China\footnote{ We are grateful for various people from various university, and several conferences for useful feedback. }

### 2024-07-02 manuscript/main.tex
modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.out 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex 	modified:   result_tables/entry_effect_hetero_1.tex 	modified:   result_tables/entry_effect_hetero_2.tex 	modified:   result_tables/formulate_the_tables.ipynb 	modified:   result_tables/heter_platform_did_1.tex 	modified:   result_tables/heter_platform_did_2.tex 	modified:   result_tables/quantile_network_formation.tex

The second hand housing transaction data was collected form \href{https://www.ke.com/city/}{beke.com} for ten cities ranging from 2016 to 2022. Initially, we filtered out transaction records exhibiting unusually high prices, identifying them as outliers that could skew the analysis. We then removed records with missing values to maintain the integrity of our dataset. We also removed any records that were listed duplicated. We finally have a data with length 1,778,647 second-hand houses.\footnote{Due to government restrictions, four of these cities did not list the transaction price for each transaction during the study period.} After cleaning the data, we constructed two research samples: one at the individual transaction level and the other at the neighborhood level. The individual transaction sample contains detailed information on each transaction, including the transaction price, transaction date, price concessions, and the number of house tours. The neighborhood-level sample aggregates transaction data at the community level, encompassing variables such as the average transaction price and the average number of house tours. Additionally, we calculated the annual number of house transactions to capture Lianjia's transaction activity within each neighborhood. This data structure enables a comprehensive analysis of the impact of offline stores on housing transactions across both individual and neighborhood dimensions.

@@

\begin{equation}
    Y_{it} = \beta_0 +  pre_2 + entry + \sum_{i=1}^3 post_i + \bf{\alpha} \bf{X}_{it} + \tau_{it} + \mu_i + \epsilon_{it}.   \label{eq:entry_effect}
\end{equation}

@@

The results presented in the table \ref{tab:entry_effect} analyze the impact of Lianjia's offline stores entering segmented markets. Prior to Lianjia's entry ($pre_2$), there is no statistically significant effect on Lianjia's transaction properties, indicating that anticipation of Lianjia's entry does not influence these metrics. Post-entry ($entry$), there is a significant 9.1\% increase in revenue, suggesting a substantial boost in Lianjia's sales. However, this effect decreases to 4.7\% in the subsequent period ($post_1$) and continues to diminish in the following periods ($post_2$ and $post_3$), indicating a gradual decline in Lianjia's performance after the initial entry period. Similarly, the number of house tours exhibits a significant 2.3\% increase during the entry period, followed by a 3.\% increase in the first post-entry period. Nonetheless, this effect lessens in $post_2$, though it remains significant in $post_3$. This trend is attributed to the impact of the COVID-19 pandemic in 2020, which significantly affected the real estate market and brokerage's operation mode.

@@

To verify the robustness of the entry effect, we classified the sample into low and high Herfindahl-Hirschman Index (HHI) groups. The results, presented in Table \ref{tab:entry_effect_robustness}, indicate that the income effect for Lianjia remains consistent across both groups. Specifically, income increases by 9.2\% during the entry period, with the effect decreasing to 5.1\% in the subsequent period for the higher HHI group, and increasing by 9.6\% during the entry period and decreasing to 4.7\% for the lower HHI group. However, a significant difference emerges in the number of house tours. The entry of Lianjia increases the number of house tours by 2.9\% for the higher HHI group and by 4.4\% for the lower HHI group. In the subsequent period, the effect diminishes for the lower HHI group, indicating that the entry of new competitors mitigates Lianjia's entry effect. Conversely, the entry effect remains significant for the higher HHI group. This analysis underscores the varying impacts of market concentration on Lianjia's market performance post-entry.

Furthermore, in columns 5 and 6, the entry of Lianjia's offline stores significantly shortens the transaction period for the higher HHI group. This suggests that offline stores enhance market efficiency by better matching buyers and sellers. Conversely, this effect is not significant in the lower HHI group, indicating that the benefits of offline stores diminish in more competitive markets. Regarding price concessions, the entry of Lianjia's offline stores does not have a significant effect in the lower HHI group initially. However, by the $post_3$ period, the effect becomes significant and positive. This delayed impact may be attributed to the offline stores gradually improving market transparency and information dissemination, which eventually leads to better price concessions. For the higher HHI group, the entry of Lianjia's offline stores consistently has a significant effect on price concessions. This reinforces the notion that in less competitive markets, offline stores play a crucial role in facilitating better matches between buyers and sellers and improving overall market efficiency. In the Appendix we also conducted the robustness check by classifying the group by matured market and less matured market. [ THERE IS ALSO A GRAPH OF PARALLEL TREND NEED TO BE ADDED HERE. ]

\begin{table}
  \begin{center}
    \begin{scriptsize}
      \caption{Robustness Check of Entry Effect}
      \label{tab:entry_effect_robustness}
      \input{../result_tables/entry_effect_hetero_1.tex}

@@

\begin{table}
  \begin{center}
    \begin{scriptsize}
      \caption{Robustness Check of Entry Effect (Continued)}
      \label{tab:entry_effect_robustness}
      \input{../result_tables/entry_effect_hetero_2.tex}

@@

We decided to use the so called quantile estimator proposed by \citep{https://doi.org/10.1111/j.1468-0262.2006.00668.x}. The CIC model does not assume that the

@@

The table shown in the Table \ref{tab:network_clustering_effect} shows the

>>>>

The second hand housing transaction data was collected form \href{https://www.ke.com/city/}{beke.com} for ten cities ranging from 2016 to 2022.\footnote{Due to government policy, Lianjia was unable to disclose transaction prices in Beijing, Shenzhen, and Wuhan for the years 2021 and 2022, as well as in Chengdu for 2021. Consequently, we have excluded this period of data for these cities from our analysis.} Initially, we filtered out transaction records exhibiting unusually high prices, identifying them as outliers that could skew the analysis. We then removed records with missing values to maintain the integrity of our dataset. We also removed any records that were listed duplicated. We finally have a data with length 1,778,647 second-hand houses.\footnote{Due to government restrictions, four of these cities did not list the transaction price for each transaction during the study period.} After cleaning the data, we constructed two research samples: one at the individual transaction level and the other at the neighborhood level. The individual transaction sample contains detailed information on each transaction, including the transaction price, transaction date, price concessions, and the number of house tours. The neighborhood-level sample aggregates transaction data at the community level, encompassing variables such as the average transaction price and the average number of house tours. Additionally, we calculated the annual number of house transactions to capture Lianjia's transaction activity within each neighborhood. This data structure enables a comprehensive analysis of the impact of offline stores on housing transactions across both individual and neighborhood dimensions.

@@

\begin{equation}
    Y_{it} = \beta_0 +  pre_2 + entry + \sum_{i=1}^3 post_i + \bf{\alpha} \bf{X}_{it} + \tau_{t} + \mu_i + \epsilon_{it}.   \label{eq:entry_effect}
\end{equation}

@@

The results presented in the table \ref{tab:entry_effect} analyze the impact of Lianjia's offline stores entering segmented markets. Prior to Lianjia's entry ($pre_2$), there is no statistically significant effect on Lianjia's transaction properties, indicating that anticipation of Lianjia's entry does not influence these metrics. Post-entry ($entry$), there is a significant 9.1\% increase in revenue, suggesting a substantial boost in Lianjia's sales. However, this effect decreases to 4.7\% in the subsequent period ($post_1$) and continues to diminish in the following periods ($post_2$ and $post_3$), indicating a gradual decline in Lianjia's performance after the initial entry period. Similarly, the number of house tours exhibits a significant 2.3\% increase during the entry period, followed by a 3.1\% increase in the first post-entry period. Nonetheless, this effect lessens in $post_2$, though it remains significant in $post_3$. This trend is attributed to the impact of the COVID-19 pandemic in 2020, which significantly affected the real estate market and brokerage's operation mode.

@@

To verify the robustness of the entry effect, we classified the sample into low and high Herfindahl-Hirschman Index (HHI) groups. The results, presented in Table \ref{tab:entry_effect_robustness_1}, indicate that the income effect for Lianjia remains consistent across both groups. Specifically, income increases by 7.9\% during the entry period, with the effect decreasing to 5.0\% in the subsequent period for the lower HHI group, which demonstrates the entry can create a very large impact on the compettive market. Moreover, the income increases by 6.8\% and 7.8\% during the entry period and decreases to insignificant after the entry period in the moderate and high concentration market. This demonstrates that Lianjia's entry can only make companies profitable in less competitive markets, and it can enhance profitability in more competitive markets. However, a significant difference emerges in the number of house tours. The entry of Lianjia increases the number of house tours by 5.4\% in the second year and 5.9\% in the third year for the low competitive group. The entry's effect is also significant, with a 3.9\% increase in the number of house tours in the second year for the high concentration market. However, this effect diminishes for the moderately competitive group. The result indicates that the results indicate that when facing other competitors in the market, Lianjia is more likely to make greater efforts to attract more sellers. This analysis underscores the varying impacts of market concentration on Lianjia's market performance post-entry.

Furthermore, in Table \ref{tab:entry_effect_robustness_2}, The entry of Lianjia's offline stores significantly shortens the transaction period for the moderate HHI group by about 5\%. Conversely, this effect is not significant in the lower HHI group and higher concentration group. This pattern suggests that when the market is highly competitive, Lianjia is not able to shorten the transaction period and in highly concentrated markets, Lianjia is also unable to use its information advantage to shorten the transaction period. Regarding price concessions, the entry of Lianjia's offline stores does not have a significant effect in the moderate HHI group initially. However, the entry of offline stores have no influence on other groups. Overall, the results suggest that the entry of offline stores has a very limited influence on consumers' welfare but can help the brokerage earn more profit. Additionally, the entry of Lianjia's offline stores can help the brokerage attract more sellers and, consequently, find more buyers in the market, thereby increasing the brokerage's informational advantage. In the Appendix we also conducted the robustness check by classifying the group by matured market and less matured market.

% This delayed impact may be attributed to the offline stores gradually improving market transparency and information dissemination, which eventually leads to better price concessions. For the higher HHI group, the entry of Lianjia's offline stores consistently has a significant effect on price concessions. This reinforces the notion that in less competitive markets, offline stores play a crucial role in facilitating better matches between buyers and sellers and improving overall market efficiency. In the Appendix we also conducted the robustness check by classifying the group by matured market and less matured market.

\begin{table}
  \begin{center}
    \begin{scriptsize}
      \caption{Robustness Check of Entry Effect}
      \label{tab:entry_effect_robustness_1}
      \input{../result_tables/entry_effect_hetero_1.tex}

@@

\begin{table}
  \begin{center}
    \begin{scriptsize}
      \caption{Robustness Check of Entry Effect (Continued)}
      \label{tab:entry_effect_robustness_2}
      \input{../result_tables/entry_effect_hetero_2.tex}

@@

We decided to use the so called quantile estimator described in model  proposed by \citep{machado_quantiles_2019}.

\begin{equation}
  \begin{aligned}
    Q_y(\xi \mid X) & = \beta_0 + \beta_1(\xi) \text{pre\_treatment}_{it} + \beta_2(\xi) \text{treatment} + \sum_{i=3}^5 \beta_i(\xi) \text{post\_treatment}_{it} \\
    & + \beta(\xi) \bf{X}_{it} + \mu_i + \tau_t + \varepsilon_{it}
  \end{aligned}
\end{equation}

\ref{tab:quantile_estimate_network} shows the quantile estimation of the . We can see that the

@@

\begin{table}
  \begin{center}
    \begin{scriptsize}
      \caption{Estimated Network Spillover Effect}
      \label{tab:estiamted_spillover_effect}
      \input{../result_tables/clustering_indices.tex}

      Note: The indices used are the Average and Global Clustering Coefficients. $*$ denotes a low network effect, which ranges from 0.3 to 0.5. $**$ indicates a moderate network effect, ranging from 0.5 to 0.75. $***$ signifies a large network effect, ranging from 0.75 to 1.
    \end{scriptsize}
  \end{center}
\end{table}

\begin{table}
  \begin{center}
    \begin{scriptsize}
      \caption{Quantile Estimation of the Network Spillover Effect}
      \label{tab:quantile_estimate_network}
      \input{../result_tables/quantile_network_formation.tex}
